%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Lisa N.}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Cao}}}}} % Last name

	\vspace{6pt}
	
	{\huge Undergraduate Student} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Burnaby, BC}\\
	\icon{Phone}{12}{+1 778 999 4798}\\
	\icon{At}{12}{\href{mailto:lisanatashacao@gmail.com}{lisanatashacao@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{http://bit.do/lnc-cv}{CV: bit.do/lnc-cv}}\\
	\icon{Github}{12}{\href{https://github.com/lisancao}{github.com/lisancao}}\\
	\icon{Twitter}{12}{\href{https://twitter.com/lisancao}{@lisancao}}\\
	
\end{minipage}

\vspace{0.15cm}
%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------
\cvsect{Who Am I?}

\begin{minipage}[t]{0.5\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
I now enjoy building open source tools for bioinformaticians after spending a few years doing bench and animal work in biobehavioural research labs. My most recent and notable achievement includes leading the winning Hackseq'19 with my project BiocSwirl. I got my tech start working as an entry level Linux SysAdmin in the nonprofit sector.
\end{minipage}
\hfill\hfill\hfill
\begin{minipage}[t]{0.25\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.25}
		\baritem{R}{40} 
		\baritem{Python}{30}
		\baritem{SQL}{30}
		\baritem{Bash}{40}
	\end{barchart}

\end{minipage}
\begin{minipage}[t]{0.2\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.25}
		\baritem{Git}{40}
		\baritem{LaTeX}{30}
		\baritem{HTML5}{30}
	\end{barchart}	
\end{minipage}
\vspace{-.5em}
\cvsect{Skills}
\vspace{-.5em}
\begin{flushleft}
\vspace{-\topsep}
	\begin{itemize}
    \itemsep-.3em
  \item[$\bullet$] {Proficiency in UNIX/Linux Systems, hardware and repository management}
  \item[$\bullet$] {Strong version control and package maintenance skills in documentation, workflow, and issue management}
  \item[$\bullet$] {Experience using standard bioinformatics tools and filetypes at the command line}  
  \item[$\bullet$] {Knowledge of human genomics, neuroinformatics, and scRNA/snRNA-seq and ChIP-seq pipelines}
  \item[$\bullet$] {Communication and presentation skills that are effective for technical subjects at beginner and advanced levels}
  \item[$\bullet$] {Ability to interpret, troubleshoot, research, and report on complex topics in computer science and biology}
	\end{itemize}
\end{flushleft}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-1em}
\cvsect{Experience}
\vspace{-.25em}
\begin{entrylist}
	\entry
		{2015 -- 2018\\\footnotesize\texttt{R}}
		{Workshop Facilitator}
		{SFU Scientific Programming Group}
		{I lead hands-on workshops for graduate students with a focus on practical skills that can be used to immediately improve research. Examples of workshops I've taught are: Introduction with Bioinformatics with R, Heatmaps in R, and Resume/CV's with RVitae.}
	\entry
		{2016 -- 2019\\\footnotesize\texttt{Benchwork}\slashsep\texttt{R}}
		{Research Assistant}
		{Sleep and Circadian Neuroscience Lab, Dr. Ralph Mistlberger}
		{Performed common laboratory neuroscience histology and biochemistry methods and gained experience with trangenic mice. I have also done data cleaning, basic data analyses, linear mixed modeling, and data visualization on behavioural time-series data.}
	\entry
		{2014 -- 2019\\\footnotesize\texttt{Benchwork}\slashsep\texttt{R}}
		{Research Assistant}
		{Behavioural Endocrinology Lab, Dr. Neil Watson}
		{Performed ELISA hormonal immunoassays on human saliva and common laboratory maintenance activities. Also worked towards improving data practices through archiving and developing a reproducible R workflow. }
	\entry
		{2014 -- 2017\\\footnotesize\texttt{Ubuntu}\slashsep\texttt{Bash}}
		{Linux System Administrator}
		{Vancouver Women's Health Collective}
		{Oversaw all hardware and software maintenance, networking, and printing for a computer lab running a mix of Windows and Ubuntu systems. Provided free, open source, and user-friendly software solutions for refurbished computers. Worked in a cross-platform environment.}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\vspace{-2em}
\cvsect{Projects}
\vspace{-.25em}
\begin{entrylist}
	\entry
		{2019 -- Present\\\footnotesize\texttt{R}\slashsep\texttt{Bash}}
		{BiocTools}
		{github.com/biocswirl-dev-team/}
		{An R package containing in-depth and easily updateable courses (BiocSwirl) used to teach entire bioinformatics workflows in R/Bioconductor using a highly configurable, lightweight and feature rich terminal interface (BiocTerm) with multi-language support. Winner of Hackseq2019.}
	\entry
		{2020\\\footnotesize\texttt{R}}
		{Visualization of Gene Expression Data}
		{STAT240 Assignment}
		{An Interactive R Shiny App that provides Kernel Density Estimations of select genes based on experimental condition using the GSE21935 dataset investigating BA22 schizophrenia indicators.}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-2em}
\cvsect{Education}
\vspace{-.25em}
\begin{entrylist}
	\entry
		{2012 -- Present}
		{Bachelor of Arts Psychology, Minor Statistics}
		{Simon Fraser University}
		{Select Schoolwork: R Shiny App for Gene Expression, Histogram Functions from Scratch, Data Analysis in R, SQL Querying, Webscraping, Introductory Python, Biology, Psychopharmacology}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\vspace{-1em}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Certifications}
	\vspace{-.5em}

	\textbf{Epigenomic Data Analysis}\\
	\textbf{CCAC Animal Lab Training}\\
	\textbf{Laboratory Safety Training}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	\vspace{-.5em}
	
	In my free time I enjoy modding video games, customizing my linux setup, performing gongfu tea ceremonies, and cooking.
	
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
    \vspace{-.5em}
    
	I am currently an organizer for Hackseq, RLadies Vancouver, Vancouver Datajam, and the SFU Scientific Programming Group.
\end{minipage}
%----------------------------------------------------------------------------------------
\end{document}
